### 2021-07-29 doc/thesis/chapters/implementation.tex
incorporate some of the feedback (wip)

Again, an audio file is used as an input, which is modulated as an FM channel signal.
The entire multiplex signal is then modulated onto an actual carrier frequency of 99 MHz, that is within the FM radio broadcast band.
This entire DSP chain is being run in the GNU Radio software, on a host PC.
Only the final signal - FM modulated, and on a carrier of 99 MHz - is then sent to the USRP device in the form of digital signal samples.
The USRP hardware then transmits the signal via its antenna.\\

>>>>

Again, an audio file is used as an input, which is modulated as an FM channel signal.
The entire multiplex signal is then modulated onto an actual carrier frequency of 99~MHz, that is within the FM radio broadcast band.
This entire DSP chain is being run in the GNU Radio software, on a host PC.
Only the final signal - FM modulated, and on a carrier of 99~MHz - is then sent to the USRP device in the form of digital signal samples.
The USRP hardware then transmits the signal via its antenna.\\
